This is an example of article title

### 2019-08-29 paper.tex
code -> texttt

\usepackage{url}
% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

@@

We implement groupby and join by traversing tables in the key-order. We use counting sort wherever possible (e.g. integer columns, PooledArrays) to do a small amount of initial work on the order of $O(k \log k)$ where $k$ is the number of unique values and then acheive a sorted permutation in $O n$ time where $n$ is the number of rows. In most systems where the implementation is done in C++, the ordering routines are restricted to a handful of primitive data types. In our system any user defined data type with an \code{isless} method to compare two items can take part in the sorting.

\textbf{Indexing: }For speeding up table operations, you can tell
JuliaDB to keep the rows of a table sorted by some of its fields.
These fields are called primary key fields. The primary key fields
can be of any data type which has an \code{isless} method associated
with it to compare two values. This includes but is not limited to
numbers, strings, symbols, dates, time periods, currencies, quantities
of comparable physical units (e.g. inch, mm).

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

@@

We implement groupby and join by traversing tables in the key-order. We use counting sort wherever possible (e.g. integer columns, PooledArrays) to do a small amount of initial work on the order of $O(k \log k)$ where $k$ is the number of unique values and then achieve a sorted permutation in $O n$ time where $n$ is the number of rows. In most systems where the implementation is done in C++, the ordering routines are restricted to a handful of primitive data types. In our system any user defined data type with an \texttt{isless} method to compare two items can take part in the sorting.

\textbf{Indexing: }For speeding up table operations, you can tell
JuliaDB to keep the rows of a table sorted by some of its fields.
These fields are called primary key fields. The primary key fields
can be of any data type which has an \texttt{isless} method associated
with it to compare two values. This includes but is not limited to
numbers, strings, symbols, dates, time periods, currencies, quantities
of comparable physical units (e.g. inch, mm).
